### 2015-12-11 paper/3-features.tex
Proofread 3.1 Conservative

We will not make a detailed comparison with PythonPDEVS here, but only mention some supported features.
Dxex supports, similarly to PythonPDEVS, the following features: direct connection~\cite{SymbolicFlattening}, \textsf{Dynamic Structure DEVS}~\cite{DSDEVS}, termination conditions, and a modular tracing and scheduling framework~\cite{PythonPDEVS}.
But whereas PythonPDEVS only supports optimistic synchronization, dxex support multiple synchronization protocols.
This is in line with the design principle of PythonPDEVS: allow users to pass performance hints to the simulation kernel.
In our case, a user can pass the simulation kernel the ``hint'' as to which synchronization protocol must be used for this model.
Our implementation in C++11 also allows for optimizations which were plainly impossible in an interpreted language.

@@

\subsubsection{Conservative}
For conservative synchronization, each node determines the nodes it is influenced by.
Each model provides a lookahead function, which determines the lookahead depending on the current simulation state.
Within this time interval, it is an error if a model raises an event, thus violating its previous promise.
The node uses this information to compute its earliest output time (EOT), and writes out the value in shared memory through the use of C++11 synchronization primitives.

In our implementation, we thus make explicit use of these new C++11 synchronization primitives.
Whereas this was also possible in previous versions of the C++ standard, it was not a part of the standard itself.
C++11 allows us to make our implementation portable, as well as more efficient: compilers might know of optimizations specific to atomic variables.

>>>>

We will not make a detailed comparison with PythonPDEVS here, but only mention some supported features.
Dxex supports, similarly to PythonPDEVS, the following features: direct connection~\cite{SymbolicFlattening}, \textsf{Dynamic Structure DEVS}~\cite{DSDEVS}, termination conditions, and a modular tracing and scheduling framework~\cite{PythonPDEVS}.
But whereas PythonPDEVS only supports optimistic synchronization, dxex support multiple synchronization protocols (though only in parallel).
This is in line with the design principle of PythonPDEVS: allow users to pass performance hints to the simulation kernel.
In our case, a user can pass the simulation kernel the ``hint'' as to which synchronization protocol must be used for this model.
Our implementation in C++11 also allows for optimizations which were plainly impossible in an interpreted language.

@@

\subsubsection{Conservative}
For conservative synchronization, each node must determine the nodes it is influenced by.
Each model needs to provide a lookahead function, which determines the lookahead depending on the current simulation state.
Within the returned time interval, the model promises not to raise an event.
A node aggregates this information to computes its earliest output time (EOT).
This value is written out in shared memory, where it can be read out by all other nodes.

Reading and writing to shared memory is done through the use of the new C++11 synchronization primitives.
Whereas this was also possible in previous versions of the C++ standard, by falling back to non-portable C functions, it was not a part of the C++ language standard.
C++11 further allows us to make the implementation portable, as well as more efficient: the compiler might know of optimizations specific to atomic variables.
